EuPPollNet: A European database of plant-pollinator networks

### 2024-10-03 Manuscript/EuPPollNet_main_text.qmd
Zenodo link

**Software format:** The database was built with the R programming language and is stored as “.rds” and “.csv” formats. The construction of the database is fully reproducible and can be accessed at the following link: <https://github.com/JoseBSL/EuPPollNet.git>.

@@

All data and code to produce of this database and manuscript are available at Zenodo (LINK) and Github (<https://github.com/JoseBSL/EuPPollNet.git>).

>>>>

**Software format:** The database was built with the R programming language and is stored as “.rds” and “.csv” formats. The construction of the database is fully reproducible and can be accessed at the following link: <https://doi.org/10.5281/zenodo.13885274>.

@@

All data and code to produce of this database and manuscript are available at Zenodo (<https://doi.org/10.5281/zenodo.13885274>) and Github (<https://github.com/JoseBSL/EuPPollNet.git>).
